Refinements for Open Automata

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
rephrase symbolic

A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation. We informally explain here the symbolic nature of the bisimulation for OA and the related complexity of its definition.
\RAB{The notion of symbolic bisimulation, as it was introduced in \cite{HENNESSY:1995}, is aimed at computing bisimulation of value-passing processes. The class of processes manipulating and exchanging with the environment data, where the values are from possibly infinite domain.}
 The presence of holes in fact raises no strong difficulty but the variables must be handled carefully.
Consider the two following simple OA:

>>>>

A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation. We informally explain here the symbolic nature of the bisimulation for OA and the related complexity of its definition.
The notion of symbolic bisimulation, as it was introduced in \cite{HENNESSY:1995}, is aimed at computing bisimulation of value-passing systems, i.e. systems made of processes exchanging data with their environment and between processes, where data are values from a possibly infinite domain.
 The presence of holes in fact raises no strong difficulty but the variables must be handled carefully.
Consider the two following simple OA:
